Semi-supervised author disambiguation of scientific publications

### 2015-07-20 paper.tex
autosave

\subsection{Overview}
% figure, notations, etc

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ and a set of authors ${\cal A} = \{ a_0, ..., a_{M-1}\}$
corresponding to individuals.  Let us define a signature $s \in p$ from a
publication as a unique piece of information identifying one of the authors of
$p$ (e.g., the author name, his affiliation, along with any other metadata can
be derived from $p$). Let us denote by ${\cal S} = \{ s | s \in p, p \in {\cal
P} \}$ the set of all signatures that can be extracted from all publications in
${\cal P}$. In this context, the author disambiguation problem can be stated as
the problem of finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of
${\cal S}$ such that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$
for all $i \neq j$, and where subsets $c_i$, or clusters, each corresponds to
the set of all signatures belonging to the same individual $a_i$. Note that in
practice, the set ${\cal A}$ often remains unknown and the task therefore boils
down to finding a partition ${\cal C}$ such that subsets   $c_i$  each
corresponds to the set of all signatures from a same individual.

>>>>

\subsection{Overview}

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
define a signature $s \in p$ from a publication as a unique piece of
information identifying one of the authors of $p$ (e.g., the author name, his
affiliation, along with any other metadata can be derived from $p$). Let us
denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
signatures that can be extracted from all publications in ${\cal P}$. In this
context, the author disambiguation problem can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Note that in practice, the
set ${\cal A}$ often remains unknown and the task therefore boils down to
finding a partition ${\cal C}$ such that subsets   $c_i$  each corresponds to
the set of all signatures from a same individual.
